\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs]{currvita}
\usepackage{ifthen}

% Initialize each paper type for which you need a bibliography.
% Just a dummy parameter is necessary.
\newcites{refpaper}{foo}
\newcites{unrefpaper}{foo}
\newcites{journal}{foo}
\newcites{techreport}{foo}
\newcites{submitpaper}{foo}
\newcites{classproject}{foo}

% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
	\begin{list}{}{%
		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
	}%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
	\begin{list}{\labelitemii}{%
		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
	}%
}%
{ \end{list} }

\begin{document}

% Specify the bibtex style that you want for each paper type
\bibliographystyle{unsrt}
\bibliographystylerefpaper{unsrt}
\bibliographystyleunrefpaper{unsrt}
\bibliographystylesubmitpaper{unsrt}
\bibliographystylejournal{unsrt}
\bibliographystyletechreport{unsrt}
\bibliographystyleclassproject{ieeetr}

% We'll use this length to change the defaults in some of our lists.
\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}

% This is what will appear at the very top of your CV.
\begin{cv}{Cheng Wei\\{\large \itshape Curriculum Vitae}}

% Items have more vertical space between them than line breaks.
\begin{cvlist}{Contact}
	\item
	Department of Computer Science\\
	School of Computing
        AS6 05-22 Multimedia System Lab\\
        Singapore, 117543
	\item Phone: +6581289359
	\item chengwe2@comp.nus.edu.sg
	% The tilde doesn't show up well in LaTeX, the \sim symbol looks
	% much better.  Though, you can't copy and paste it from your PDF
	% like you can with a tilde.
	\item http://www.comp.nus.edu.sg/$\sim$chengwe2/
\end{cvlist}

\begin{cvlist}{Research Interests}
	\item 3D Streaming, Virtual Environment, 
              Multimedia System, Distributed System,
              Peer-to-Peer System.
\end{cvlist}

\begin{cvlist}{Education}
	\item \emph{Ph.D., Computer Science}, in progress 
	National University of Singapore\\
        Singapore
	% Sublists don't have any extra vertial space.
	\end{sublist}
	\item \emph{M.S., Computer Science}, 2005\\ 
	Fudan University\\
	Shanghai, China
	%\begin{sublist}
	%	\item Thesis: \textit{Minimizing Energy Consumption in Sensor
	%	Networks Using a Wakeup Radio}
	%	\item Adviser: Prof. Nitin H. Vaidya
	%\end{sublist}
	\item \emph{B.S., Civil Engineering}, 1996\\
	Tongji University\\
	Shanghai, China
	%\begin{sublist}
	%	\item GPA: 4.0/4.0
	%	\item Minors: \emph{Computer Science} and \emph{Mathematics}
	%\end{sublist}
\end{cvlist}

%\begin{cvlist}{Honors}
%\item
	%\emph{US National Science Foundation Fellowship}
	%\begin{sublist}
	%\item Awarded in 2001
	%\item Acceptance Percentage: 16.2\% (903/5560)
	%\end{sublist}
%\item
	%\emph{ASEE National Defense Science and 
	%Engineering Graduate Fellowship}
	%\begin{sublist}
	%\item Awarded in 2001
	%\item Acceptance Percentage: 21.3\% (285/1339)
	%\end{sublist}
%\end{cvlist}

% After you have finished your CV, you may need to manually insert
% some pagebreaks to make it look nice.
\pagebreak

% cvlist items can take dates as a parameter.
\begin{cvlist}{Employment}
	\item[11/2007--8/2007] Part Time Teaching Assistant\\
	National of University of Singapore\\ 
	Singapore
	\item[6/2005--7/2005]  
	(\textit{tenure excluded summer months})\\
	Michelin, North America\\
	Greenville, SC
\end{cvlist}

% These commands will make our papers be indented after the first line
% to make the author's name stand out more.  Also, we reduce the
% indentation of the paper type titles (e.g., Journal Papers,
% Conference Paper) compared to regular cvlist items.
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}
% Do bibaddtoleftmargin instead of biblabelsep if you're
% not using manybib or open bib
%\renewcommand*{\bibaddtoleftmargin}{1.5em}
\renewcommand*{\biblabelsep}{1.5em}

% To update, before doing latexmk, run:
% bibtex journal
% bibtex refpaper
% bibtex unrefpaper
% bibtex techreport
\begin{cvlist}{Publications}
	% With multibib, each cite command has the type after it.
	\item \textbf{Journal Papers}
	\nocitejournal{miller04mac_vitae}
	\bibliographyjournal{vitae}
	\item \textbf{Conference Papers} 
	\nociterefpaper{miller06leveraging_vitae}
	\nociterefpaper{miller05improving_vitae}
	\nociterefpaper{miller05exploring_vitae}
	\nociterefpaper{miller04power_vitae}
	\nociterefpaper{miller04minimizing_vitae}
	\bibliographyrefpaper{vitae}
	\item \textbf{Submitted Papers} 
	\nocitesubmitpaper{sengul05exploring_vitae}
	\nocitesubmitpaper{miller05using_vitae}
	\bibliographysubmitpaper{vitae}
	\item \textbf{Technical Reports} 
	\nocitetechreport{miller05errata_vitae}
	\nocitetechreport{miller04ondemand_vitae}
	\nocitetechreport{miller03hybrid_vitae}
	\bibliographytechreport{vitae}
\end{cvlist}
% Reset the label indentation
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Research Experience}
	\item \textbf{Graduate Work}
	\begin{sublist}
		\item 
		My work focuses on \textit{security} and \textit{energy efficiency}
		in wireless
		multihop networks, particularly sensor networks.  In the
		security domain, I proposed a key distribution protocol to
		provide symmetric, pairwise keys that, with high
		probability, are unknown to eavesdroppers.  This was the first
		work to use the underlying wireless channel diversity
		to address this problem.  In the energy efficiency domain, most
		power save protocols use static sleeping and listening intervals
		regardless of the network environment.  My work looks at
		adaptively adjusting these intervals in response to
		network traffic.  Additionally, I have proposed methods of using
		carrier sensing to further improve the energy efficiency of
		power save protocols and a lightweight protocol to address the
		energy-latency tradeoff for broadcast dissemination in sensor
		networks.
	\end{sublist}

	\item \textbf{Graduate Class Projects}
	% This sublist looks better with bullets.
	\begin{subbulletlist}
		\item \textit{Exploring the Energy-Latency Trade-off of Broadcasts
		in IEEE 802.11 Power Save Networks}\\
		Joint work with Cigdem Sengul in Fall 2003.  
		Designed, analyzed, simulated, and evaluated (using \textit{ns-2}) 
		a protocol for power save networks and the 
		impact of its parameters on energy and latency.  Selected by the
		professor as one of the three best two-person projects in the
		class.  Published in IEEE ICDCS 2005.
		\item \textit{Improving Fault Tolerance in AODV}\\
		Joint work with Jungmin So in Fall 2002.  Designed, simulated,
		and evaluated (using \textit{ns-2})
		techniques to maintain multiple routes in an ad-hoc routing protocol.
		\item \textit{Improving Connectivity in a Scatternet Formation
		Algorithm}\\
		Joint work with Cristina L. Abad in Spring 2002.  Designed,
		simulated, and evaluated (using a custom built simulator written
		in C) a protocol to provide greater
		connectivity in Bluetooth scatternet formation. 
		\item \textit{Log Correlation for Intrusion Detection}\\
		Group project in Spring 2003.  Investigated how information 
		from various system
		logs can be used to identify specific attacks.  Subsequent work 
		by some group members led to a publication based on the
		project:  
		\renewcommand*{\biblabelsep}{1.5em}
		\nociteclassproject{abad03log}
		\bibliographyclassproject{vitae}
		\item \textit{Tools for Middle School Students to Create Vignettes}\\
		Joint work with Jeffrey Naisbitt and Naomi Caldwell in Spring
		2003.  Designed, implemented, and did user-testing on a
		tool (using Java Swing) to allow students to create life 
		stories using an instant messenger-like interface.
	\end{subbulletlist}
	\item \textbf{Awards}
	\begin{subbulletlist}
		\item NSF Student Travel Grant (US \$500) for IEEE BROADNETS 2004 
		\item NSF Student Travel Grant (US \$750) for ACM SenSys 2004
		\item DARPA/NSF Student Travel Grant (US \$400--750) for IEEE MASS 2005
	\end{subbulletlist}
\ifthenelse{\boolean{doResearchInterests}} {
\pagebreak
}{}
	\item \textbf{Undergraduate Work}
	\begin{subbulletlist}
		\item Participated in the NSF-funded Summer Undergraduate 
		Research Experience (SURE) at Clemson University in 1999.
		\item Worked in Parallel Architecture Research Lab (PARL) 
		at Clemson University for two years.
		\item Projects included designing user interfaces (using Java Swing)
		for scientific
		computing problem solving environments to allow message passing
		between modules and array partitioning.
	\end{subbulletlist}
	\item \textbf{External Reviewer}
	\begin{sublist}
		\item \textit{IEEE Transactions on Mobile Computing}, 
		\textit{IEEE Transactions on Wireless Communications}, 
		\textit{IEEE Transactions on Information Forensics and
		Security}, \textit{IEEE Communications Magazine}, 
		MobiQuitous 2004, IEEE WCNC 2004, IEEE ICC 2005, and MASS 2006  
	\end{sublist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Memberships}
	\item[1997--present] Student Member, Institute of Electrical and
	Electronics Engineers (IEEE)
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Technical Skills}
	\item \textbf{Proficient}
	\begin{sublist}
		\item C, Java, Perl, LaTeX, Matlab, 
		\textit{ns-2} Network Simulator (C++ based), TinyOS/TOSSIM (NesC)
	\end{sublist}
	\item \textbf{Familiar} 
	\begin{sublist}
		\item Tcl/Tk, ML, Prolog, Lisp, PHP
	\end{sublist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Extracurricular}
	\item[2004--2005] Large Group Coordinator\\
	UIUC Graduate InterVarsity Christian Fellowship
	\begin{subbulletlist}
	\item Responsible for contacting and scheduling about 20 
	speakers 
	\item Responsible for arranging facility and equipment
	reservations
	\item Helped restructure the chapter budget
	\end{subbulletlist}
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Miscellaneous}
\item \textit{Citizenship:} United States of America
\item \textit{Marital Status:} Married
\item \textit{Erd\"{o}s Number:} $\leq 4$
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\end{cv}
\end{document}

